### 2021-10-06 letter/letter.Rmd
change cover letter

I am writing to submit our manuscript entitled "Legislature Size and Welfare: Evidence from Brazil" for consideration as an \textit{American Journal of Political Science} research article. We present a game theory model showing that larger city councils increase local public goods provision. Partisanship is the main mechanism we explore in our article. Our evidence comes from exogenous changes in Brazilian electoral legislation, which granted additional legislators to hundreds of municipalities based on population thresholds. Our regression discontinuity models indicate that increasing local legislatures leads to higher primary school enrollment and lower infant mortality rates without any significant decrease in the quality of public service. We also survey former city councilors and analyze the content of 346,553 bills to provide further evidence for our mechanism.

@@

We also provide extensive supplementary material with data, code, and additional analyses, for consultation on \href{https://github.com/umbertomig/legislature-size-welfare}{this GitHub repository}. The appendix describes our model and data sources in detail, and it also includes a series of additional tests that show the robustness of our results.

>>>>

I am writing to submit our manuscript entitled "Legislature Size and Welfare: Evidence from Brazil" for consideration as an \textit{American Journal of Political Science} research article. We present a game theory model showing that larger city councils increase local public goods provision. Partisanship is the main mechanism we explore in our article. Our evidence comes from exogenous changes in Brazil's electoral legislation, which granted additional legislators to hundreds of municipalities based on population thresholds. Our regression discontinuity models indicate that increasing local legislatures leads to higher primary school enrollment and lower infant mortality rates without any significant decrease in the quality of public service. We also survey former city councilors and analyze the content of 346,553 bills to provide further evidence for our mechanism.

@@

We also provide extensive supplementary materials to accompany the manuscript. They are available for consultation on \href{https://github.com/umbertomig/legislature-size-welfare}{this GitHub repository}. The appendix describes our model and data sources in detail, and it also includes a series of additional tests to demonstrate the robustness of our findings.
